\thetitle

### 2024-11-28 paper/paper.tex
Account for the stretching of space
After a confirmation from A. Riess that time dilation is addressed, I
started considering if there might be a third cause for dimming. And
yes, there is.

\def \thetitle {Correcting supernova luminosity for time dilation implies no dark energy}
\title{\thetitle}

@@

\begin{abstract}
  Existing analysis of Type Ia supernova relies on the assumption that
  luminosity is not affected by time dilation. However, when luminosity is
  corrected for time dilation, the relationship between luminosity distance and
  redshift for Type Ia supernova becomes linear. This indicates that the
  expansion rate of the universe is not accelerating and there is no need for
  dark energy to explain observational data.
\end{abstract}

>>>>

\def \thetitle {Correcting supernova luminosity for stretched space implies no dark energy}
\title{\thetitle}

@@

\begin{abstract}
  Estimating the distant to Type Ia supernova requires that luminosity be
  corrected for various sources of dimming associated with redshift. The first
  source of dimming is due to the redshifting of a photon's wavelength, and
  this is addressed by a nuance of how CCD cameras collect light. The second
  source of dimming is time dilation. A third source of dimming is due to the
  stretching of space -- as space expands, light needs to travel farther to
  traverse the extra space. When reported magnitudes for Type Ia supernovae are
  corrected by an additional factor of $1 + z$, the relationship between
  luminosity distance and redshift for Type Ia supernova becomes linear. This
  indicates that the expansion rate of the universe is not accelerating and
  there is no need for dark energy to explain observational data.
\end{abstract}
